\Large \bf \vrsdust{0.7cm} \hspace{0.1in} Redstone: a Modular Deterministic Simulation Testing Framework for Distributed Systems

### 2024-06-07 paper/paper.tex
System call interception coverage

>>>>

\section{\txtrsdust System Call Interception Coverage}

{\fontsize{12}{15}\selectfont 
In the process of implementing Redstone,
we have encountered limitations to the extent and nature of what we can properly intercept and handle.
These fall into three categories:
that coverage which may be attained with sufficient work,
that coverage which is conditionally possible depending on the workload,
and that which is impossible.

The first category,
that coverage which may be attained with sufficient work
contains features like \texttt{epoll}, \texttt{select}, \texttt{poll}, \texttt{io\_uring},
more exotic network protocols,
and additional fault classes and more sophisticated fault injection algorithms.
These can be implemented given sufficient additional time investment.

The second category,
that coverage which is conditionally possible depending on the workload,
is more interesting, and perhaps the most common example is that of \texttt{getrandom}.
Given that Redstone's entire reason for existence is to be as deterministic as possible,
the naive approach would be to forward to a simulated CPRNG, such as ChaCha20,
that is seeded by some derivation of the simulation seed.
Unfortunately, if a program uses randomness for cases like cryptographic key generation,
and any kind of external accesses occur,
this indicates the presence of a significant security vulnerability due to reused keys.
As such,
randomness remains unimplemented,
and should only really be implemented assuming we can guarantee that a vulnerability will not occur on a given program.

The third category,
that which is impossible,
is introduced by restrictions on userspace.
\texttt{mmap} is the prime example of this category.
We have no way of replacing the page-in/page-out handling so this is also left as a passthrough.
